\subsection{Introduction}\label{subsec:introduction}
\begin{definition}
 An \textbf{Alphabet} is a finite, non-empty set of atomic symbols.
\end{definition}

\begin{definition}
 A \textbf{word} or \textbf{string} is any finite sequence of symbols from an alphabet. 
\end{definition}

\begin{definition}
 The \textbf{length} of a string, $s$, denoted $|s|$, is the number of symbols in $s$. 
\end{definition}

\begin{definition}
 Given strings $s=s_1s_2\hdots s_n$ and $t=t_1t_2\hdots t_m$, their \textbf{concatenation} is defined 
 
 \[s\cdot t=s_1s_2\cdots s_nt_1t_2\cdots t_m\]
\end{definition}

We denote by $\varepsilon$ the \textbf{empty string}, the unique string of 0 characters. 

\begin{definition}
 Let $A$ be any alphabet. The \textbf{Kleene Closure} of $A$, denoted $A^*$, is the set of all strings of any length over $A$.  
\end{definition}

\begin{theorem}
 Let $A$ be any finite set. Then $A^*$ is countably infinite. 
\end{theorem}

\begin{proof}
 That $A^*$ is infinite is straightforward: since $A$ is non-empty, take $a\in A$. Then $\{a, aa, aaa, \hdots\}\subseteq A^*$.
 
 To see that it is countable, we first write $|A|=n$. Now, consider the set of all strings of length 0. This is simply $\{\varepsilon\}$. Moreover, there are $n$ strings of length 1, $n^2$ strings of length 2, $n^3$ strings of length 3, and so on. Thus, we map $\varepsilon$ to 0, the strings of length 1 to $1, 2, \hdots, n$, the strings of length 2 to $n+1, n+2, \hdots, n+n^2$, the strings of length 3 to $n+n^2+1, n+n^2+2,\hdots, n+n^2+n^3$, and so on. This is a bijection from $A^*$ to $\mathbb{N}$, which completes the proof.
\end{proof}

\begin{definition}
 Given an alphabet $A$, a \textbf{formal language} or simply \textbf{language} $L$ is any subset of $A^*$. 
\end{definition}

\begin{theorem}
 Given an alphabet $A$, the set of languages over $A$ is uncountable. 
\end{theorem}

\begin{proof}
 Suppose, by way of contradiction, that the set of languages were countable, i.e., that we can enumerate the set as $\{L_1, L_2, L_3, \hdots\}$. Consider the set of all strings $\{s_1, s_2, s_3, \hdots\}$. Let $L$ be the language defined as follows: 
 
\[s_i\in L\text{ if and only if } s_i\not\in L_i\]

 To see that $L$ is not in the above list, consider $s_i$. If $s_i$ is in $L$, then $s_i$ is not in $L_i$, by construction, and $L\neq L_i$. Similarly, if $s_i$ is not in $L$, then $s_i$ must be in $L_i$, by construction, and $L\neq L_i$. In other words, for all $i$, $L\neq L_i$. Then $L$ is not in the above list, which is a contradiction. Hence, the set of languages is uncountable. 
\end{proof}

All set operations, such as union, intersection, complement, set-difference, etc. can be applied to languages, since languages are simply subsets of a Kleene Closure of an alphabet.

\begin{definition}
 Given two languages $L_1$ and $L_2$, the concatenation $L_1\cdot L_2$ is given by
 
 \[L_1\cdot L_2=\{s\cdot t|s\in L_1\text{ and } t\in L_2\}\]
\end{definition}

Clearly, we have 

\begin{align*}
    L\cdot\emptyset &= \emptyset = \emptyset\cdot L\\
    L\cdot\{\varepsilon\} &= L = \{\varepsilon\}\cdot L
\end{align*}

Note that $L_1\cdot L_2$ is not the same as $L_1\times L_2$. Let $L_1=L_2=\{\varepsilon, 0, 00\}$. Then

\[L_1\times L_2=\{(\varepsilon, \varepsilon), (\varepsilon, 0), (\varepsilon, 00), (0, \varepsilon), (0, 0), (0, 00), (00, \varepsilon), (00, 0), (00, 00)\}\]

whereas 

\[L_1\cdot L_2=\{\varepsilon, 0, 00, 000, 0000\}\]

\begin{definition}
 Given a language $L$, the \textbf{Kleene Closure} of $L$, $L^*$, is 
 
 \[L^*=\bigcup_{i=0}^{\infty}L^i\]
 
 where \[L^i = \begin{cases} \{\varepsilon\} &\mbox{if } i = 0 \\
L \cdot L^{i-1} & \mbox{otherwise }\end{cases}\]
\end{definition}

Note that, while $0^0$ is normally left undefined, we define $\emptyset^0=\{\varepsilon\}$.

\begin{theorem}
 $L^*$ is finite if and only if $L=\emptyset$ or $L=\{\varepsilon\}$.
\end{theorem}

\begin{proof}
 If $L=\emptyset$, then $L^i=\emptyset^i=\emptyset$ for $i>0$. Then 
 
 \begin{align*}\emptyset^*&=\bigcup_{i=0}^{\infty}\emptyset^i\\
                          &=\emptyset^0\cup\bigcup_{i=1}^{\infty}\emptyset^i\\
                          &=\{\varepsilon\}\cup\bigcup_{i=1}^{\infty}\emptyset\\
                          &=\{\varepsilon\}
\end{align*}

Similarly, if $L=\{\varepsilon\}$, then $L^i=\{\varepsilon\}$ for all $i$, and 

 \begin{align*}\{\varepsilon\}^*&=\bigcup_{i=0}^{\infty}\{\varepsilon\}^i\\
                          &=\bigcup_{i=1}^{\infty}\{\varepsilon\}\\
                          &=\{\varepsilon\}
\end{align*}

However, if $L$ is neither $\emptyset$ nor $\{\varepsilon\}$, then there exists a string $s\in L$ with length at least 1. Then $s, ss, sss, \hdots$, are in $L^*$, hence $L^*$ is infinite.
\end{proof}